### 2025-05-22 skripsi/chapter4.tex
fix dagger in pseudocode for lssvr training since we just do least squares and not psuedoinverse, add footer, add signatures

Next we present the results of comparing our model in for solving the IVP for the Burgers' Equation against the method of lines and finite differences using SciPy odeint, torchdiffeq odeint, NumPy gradient, and PyTorch gradient. First, we present the results of solving \lccref{eq:burgers_exact_solution} as an IVP as shown in \lccref{table:comparison_exact_metrics_0.1} for viscosity \(\nu=0.1\). For the forcing term, we use a constant value of zero. The functions are also unperturbed. The metrics measure the performace of the predicted solutions compared against the exact solution. We see that our model has slightly better performance compared to the lsoda method. We do want to note that for lower viscosity values the lsoda method performs much better compared to ours as shown in \lccref{sec:burgers_comparison}. And for the viscosity of \(\nu=0.0\), even the IABM method performs much better due to the fact that the solution is a constant value of zero. The baseline FNN method, however, does not perform well on any of the viscosities with the solution becoming unstable after several time steps.
\begin{table}[H]
  \caption{Metrics for predicting the exact solution for each method with viscosity \(\nu=0.1\)}\label{table:comparison_exact_metrics_0.1}
  \centering
  \begin{tabular}{lcccc}
    \toprule
    Method            & MSE  & RMSE & MAE  & sMAPE \\
    \midrule
    SpectralSVR       & 0.00 & 0.02 & 0.02 & 1.47  \\
    SpectralSVR (FNN) & inf  & inf  & inf  & 1.98  \\
    lsoda             & 0.00 & 0.03 & 0.02 & 1.56  \\
    IABM              & nan  & nan  & nan  & nan   \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

Next we present the results of comparing our model in for solving the IVP for the Burgers' Equation against the method of lines and finite differences using SciPy odeint, torchdiffeq odeint, NumPy gradient, and PyTorch gradient. First, we present the results of solving \lccref{eq:burgers_exact_solution} as an IVP as shown in \lccref{table:comparison_exact_metrics_0.1} for viscosity \(\nu=0.1\). For the forcing term, we use a constant value of zero. The functions are also unperturbed. The metrics measure the performance of the predicted solutions compared against the exact solution. We see that our model has slightly better performance compared to the lsoda method. We do want to note that for lower viscosity values the lsoda method performs much better compared to ours as shown in \lccref{sec:burgers_comparison}. And for the viscosity of \(\nu=0.0\), even the IABM method performs much better due to the fact that the solution is a constant value of zero. The baseline FNN method, however, does not perform well on any of the viscosity values with the solution becoming unstable after several time steps.
\begin{table}[H]
  \caption{Metrics for predicting the exact solution for each method with viscosity \(\nu=0.1\)}\label{table:comparison_exact_metrics_0.1}
  \centering
  \begin{tabular}{lcccc}
    \toprule
    Method            & MSE  & RMSE & MAE  & sMAPE \\
    \midrule
    SpectralSVR       & 0.00 & 0.02 & 0.02 & 1.47  \\
    SpectralSVR (FNN) & inf  & inf  & inf  & 1.98  \\
    lsoda             & 0.00 & 0.03 & 0.02 & 1.56  \\
    IABM              & nan  & nan  & nan  & nan   \\
    \bottomrule
  \end{tabular}
\end{table}
